Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-11 tex/MesnardoBarba2019.tex
edits final section
(We still need a concluding paragraph.)

\begin{figure*}[!h]
    \centering
    \includegraphics[width=16cm]{figures/qcrit_wx_wake3d_0020.png}
    \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1.0$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$. The isosurfaces are colored with the streamwise vorticity ($-5 \leq w_x c / U_\infty \leq 5$). The figure was generated using the visualization software VisIt \cite{childs_et_al_2012}.}
    \label{fig:qcrit_wx_3d}
\end{figure*}

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).

@@

Command-line utilities such as Azure-CLI and Batch Shipyard were greatly helpful to create and manage resources on Microsoft Azure to conduct reproducible research.
(In our lab, we tend to avoid interacting directly with graphical-user interfaces to keep a trace of the commands run and make the workflow more reproducible.)
Azure-CLI helped us setup the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
Thanks to Batch Shipyard, we did not have to dig into the software development kit of Azure Batch to use the service.
Writing YAML configuration files was all we needed to create a pool of virtual machines with Batch Shipyard and to submit jobs to it.
With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers; everything from the command-line terminal on a local machine.
Note that Bach Shipyard also support Singularity containers.

Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
The Poisson system is solved on distribute GPU devices using the NVIDIA AmgX library.
Thus, we have used Azure instances of the NC-series that feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.

Moreover, Microsoft Azure implements quotas and limits on resources with Azure Batch service, such as the maximum number of dedicated cores that can used in a certain region.
To be able to run our simulations, we had to contact Azure Support through Azure Portal to request a quota increase for a given type of instances in a specific region and for a given subscription.
We had to go through this process at least five times during our sponsorship period.
The readers should be aware of these quotas and limits before scaling up workloads on Azure Batch.

In a new effort to make our research transparent and reproducible by others, we have version-controlled all the files necessary to re-run the examples highlighted in this paper.
The repository \texttt{cloud-repro}\footnote{\url{https://github.com/barbagroup/cloud-repro}} is hosted on GitHub.
The reproducibility packages contains input files, Batch Shipyard configuration files, command-line instructions to setup and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
Although they are not required to reproduce the computations, the Dockerfiles to build Docker images are also made available.
These files contain details about the all libraries installed to create the computational runtime environment.
In addition, we have also uploaded to Zenodo all output data required to just reproduce the figures of the present paper.

@@

This study was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.

>>>>

\begin{figure*}[!h]
    \centering
    \includegraphics[width=18cm]{figures/qcrit_wx_wake3d_0020.png}
    \caption{Lateral view of the isosurfaces of the Q-criterion ($Q = 1.0$) in the wake of the snake cylinder (with a $35$-degree angle of attack) at Reynolds number $2000$. The isosurfaces are colored with the streamwise vorticity ($-5 \leq w_x c / U_\infty \leq 5$). The figure was generated using the visualization software VisIt \cite{childs_et_al_2012}.}
    \label{fig:qcrit_wx_3d}
\end{figure*}

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).

@@

Command-line utilities such as Azure-CLI and Batch Shipyard were of great help to create and manage resources on Microsoft Azure for executing our reproducible research workflow.
(In our lab, we tend to avoid interacting directly with graphical-user interfaces to keep a trace of the commands run and make the workflow more reproducible.)
Azure-CLI helped us set up the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
Thanks to Batch Shipyard, we did not have to dig into the software development kit of Azure Batch to use the service.
Writing YAML configuration files was all we needed to do to create a pool of virtual machines with Batch Shipyard and to submit jobs to it.
With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers, everything from the command-line terminal on a local machine.
Note that Bach Shipyard also supports Singularity containers.

Our in-house CFD software, PetIBM, relies on MPI to run applications on distributed-memory architectures.
The Poisson system is solved on distributed GPU devices using the NVIDIA AmgX library.
Thus, we used Azure instances of the NC-series, which feature a network interface for remote direct memory access (RDMA) connectivity, allowing nodes in the same pool to communicate over InfiniBand network.
As of this writing, only Intel MPI 5.x versions are supported with the Azure Linux RDMA drivers.

Microsoft Azure implements quotas and limits on resources with Azure Batch service, such as the maximum number of dedicated cores that can used in a certain region.
To be able to run our simulations, we had to contact Azure Support through Azure Portal to request a quota increase for a given type of instances in a specific region and for a given subscription.
We had to go through this process at least five times during our sponsorship period.
The readers should be aware of these quotas and limits before scaling up workloads on Azure Batch.

In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
The repository is found at \url{https://github.com/barbagroup/cloud-repro}.

Our expanded reproducibility packages contain input files, Batch Shipyard configuration files, command-line instructions to set up and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
Although they are not required to reproduce the computations, the Dockerfiles to build Docker images are also made available. 
These files contain details about all the libraries needed to create the computational runtime environment.
We even included a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
In addition, we have also deposited in the Zenodo service all secondary data required to reproduce the figures of the paper without running the simulations again.

@@

This work was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.
